\textls[-0]{\thetitle}

### 2023-03-24 metatheory2.tex
resolve a comment

Unlike in \cref{sec:metatheory2}, which uses named binders, in this appendix we
use \citeauthor{debruijn1964} indices and \emph{explicit
substitutions}~\cite{abadi1989subst,substcalculus}:
substitutions~$\gm$ and their applications (e.g., \sub{T}{\gm}, which
applies~$\gm$ to the type~$T$) are part of the syntax rather than
meta-operations.
We work in an intrinsically typed setting: terms are well typed by construction, 
%
and consequently some premises are omitted without ambiguity and can be inferred from the context. \EDJ{I added this sentence back here. Why removed this sentence earlier?}\YZreply{I don't find a strong causal connection between the two parts of the sentence}\EDJreply{If it is not intrinsically typed (everything is raw), then no inference can be done.}
% 
This style of syntax formulation follows a recent
trend~\cite{altkap2016,coquand2018canonicity,gratzer-sterling-birkedal-2019}
known as the ``algebraic presentation'' of MLTT.
%We introduce judgmental equality ($\equiv$)
%for derivations (of all kinds of judgements). In other words, we will have judgemental equality between terms, 
%contexts, explicits substitutions, and etc. 
%This style of syntax formulation has been carried out by the recent trend~\cite{altkap2016,coquand2018canonicity,gratzer-sterling-birkedal-2019} dubbed as ``algebraic presentation'' of MLTT. 
Moreover, universe levels are explicit in this appendix.

>>>>

Unlike in \cref{sec:metatheory2}, which uses named binders, in this appendix we
use \citeauthor{debruijn1964} indices and \emph{explicit
substitutions}~\cite{abadi1989subst,substcalculus}:
substitutions~$\gm$ and their applications (e.g., \sub{T}{\gm}, which
applies~$\gm$ to the type~$T$) are part of the syntax rather than
meta-operations.
We work in an intrinsically typed setting: terms are well typed by construction.
%
Consequently, we omit without ambiguity some obvious premises needed for well-formedness.
% 
This style of syntax formulation follows a recent
trend~\cite{altkap2016,coquand2018canonicity,gratzer-sterling-birkedal-2019}
known as the ``algebraic presentation'' of MLTT.
%We introduce judgmental equality ($\equiv$)
%for derivations (of all kinds of judgements). In other words, we will have judgemental equality between terms, 
%contexts, explicits substitutions, and etc. 
%This style of syntax formulation has been carried out by the recent trend~\cite{altkap2016,coquand2018canonicity,gratzer-sterling-birkedal-2019} dubbed as ``algebraic presentation'' of MLTT. 
Moreover, universe levels are explicit in this appendix.
